Report on the Third Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE3)

### 2016-02-05 WSSSPE3/report/wg_appendix_training.tex
changes to changes in 5.7, H, and I

While little training focuses specifically on sustainable
software, a variety of training activities increase researcher awareness 
and engagement with software engineering practices and software professionals.
Research Software Engineers are being recognized as critical contributors to
high quality research; the pathway to acquire and master the relevant skills
is not yet clear; equally those skills required by researchers in general are
also not commonly understood nor routinely developed.

>>>>

While little training focuses specifically on sustainable
software, a variety of training activities increase researcher awareness of
and engagement with software engineering practices and software professionals.
Research Software Engineers are being recognized as critical contributors to
high quality research; the pathway to acquire and master the relevant skills
is not yet clear; equally those skills required by researchers in general are
also not commonly understood nor routinely developed.

### 2016-02-05 WSSSPE3/report/wg_main_training.tex
changes to changes in 5.7, H, and I

Next steps were identified to quickly test whether there is interest in
establishing a community committed to increasing the degree of coordination
across training projects. See Appendix~\ref{sec:appendix_training} for more
details about the discussion.

>>>>

Some next steps were identified to quickly test whether there is interest in
establishing a community committed to increasing the degree of coordination
across training projects. See Appendix~\ref{sec:appendix_training} for more
details about the discussion.
